### 2014-11-02 docs/ms.Rmd

##Abstract
```{r, eval = TRUE, echo = FALSE}
x <- rnorm(200, 0, 1)
x
```

`r round(mean(x), digits = 2)`

##Introduction
Since Thayer (1909), Poulton (1890) and Wallace (YEAR) generations of biologists have endeavored to explain the mechanisms and functions of animal and plant coloration. For these biologists, identifying best practice in measuring color and color pattern and in determining how other species see colour has been a great challenge. Over the past 150 years biologists, both independently and in collaboration with physicists and chemists, have sought out and created methods that have enabled some remarkable discoveries (Lythgoe 1979 Shout out to Endler here?). These include, for example, the fundamental differences between human color vision and that of other animals (Bennett 1994) and the ubiquity of ultraviolet coloration in birds (Eaton & Lanyon 2003). Today, the range of techniques used in research for measuring coloration are diverse and encompass spectrophotometry (also called spectroradiometry, spectroscopy ETC), photography, visual modeling.

@@

Measuring reflectance spectra is now a reasonably inexpensive and convenient technique. Spectrophotometry allows with capture of quantitative and arguably repeatable data and has been rapidly taken up by researchers the field. However one drawback to spectrophotometry, is the ease with which erroneous data can be captured if attention is not paid to finer details of spectrum capture. For example, the angle from which spectra are taken (Santos & Lumeij, 2007), consistent calibration of light and dark standards, the distance between light source and object, the expectations of the researcher and the size, shape, glossiness or iridescence of the specimen (Andersson and Prager, 2006, Schaefer et al., 2008, Kemp, Reznick & Grether, 2008, Meadows et al 2011), can all contribute to potentially skewed data or alter results. Experience, guidance and objectivity are necessary to ensure data are consistent and representative of the subject and to ensure repeatability the conditions under which data were collected must be reported exactly. In conjunction with spectrophotometry, digital photography is increasingly being implemented in color quantification. High-resolution cameras are now inexpensive and portable, allow instantaneous sampling of multiple colour patches, and can produce highly repeatable images (McKay 2013). The main challenges for gathering and using color data from photographs are ensure correct standardization methods such as linearization and consistent lighting (Stevens et al. 2007; ref Dariella Whitiyev 2014’s paper). Crucially, most digital cameras used in color science are consumer products designed for human visual color space and hardware modifications for ultraviolet and infrared imaging are necessary (e.g. Chiao et al. 2009, McKay 2013), making photography complementary, rather than superior to spectrophotometry.

@@

##What is reporting like in the literature? (what do people do?)

To determine the current state of methods reporting in the field we searched for papers from 2013 in 20 journals (see Table X): We used the Boolean search terms colour*, color* or spectra* and searched for these in the title or abstract from each of the journal’s home pages. Our search returned a total of X papers in X journals. To review the large number of papers returned from the searches, journals were haphazardly divided up between the authors. Upon reading abstracts we determined which studies took empirical measures of colour (via photography or spectrophotometry) and discarded those that did not. In order to reduce the risk of observer bias in our scoring. Papers were then read and reassessed by a second author and a third, three times in total. Any discrepancies between the assessor scores and the inclusion of papers with more obscure or uncommon methodologies, were discussed and agreed upon. We then tabulated what details of the methods were reported against our criteria.

>>>>

##Abstract

##Introduction
Since Thayer (1909), Poulton (1890) and Wallace (YEAR) generations of biologists have endeavored to explain the mechanisms and functions of animal and plant coloration. For these biologists, identifying best practice in measuring color and color pattern and in determining how other species see colour has been a great challenge. Over the past 150 years biologists, both independently and in collaboration with physicists and chemists, have developed a range of techniques used to measure and analyse animal and plant coloration including spectrophotometry (also called spectroradiometry, spectroscopy ETC), photography and visual modeling.

@@

Measuring reflectance spectra is now a reasonably inexpensive and convenient technique. Spectrophotometry allows the capture of quantitative and arguably repeatable data and has been rapidly taken up by researchers the field. However one drawback to spectrophotometry, is the ease with which erroneous data can be captured if attention is not paid to finer details of spectrum capture. For example, the angle from which spectra are taken (Santos & Lumeij, 2007), consistent calibration of light and dark standards, the distance between light source and object, the expectations of the researcher and the size, shape, glossiness or iridescence of the specimen (Andersson and Prager, 2006, Schaefer et al., 2008, Kemp, Reznick & Grether, 2008, Meadows et al 2011), can all contribute to potentially skewed data or alter results. Experience, guidance and objectivity are necessary to ensure data are consistent and representative of the subject and to ensure repeatability, conditions under which data were collected must be reported exactly.

In conjunction with spectrophotometry, digital photography is increasingly being implemented in color quantification. High-resolution cameras are now inexpensive and portable, allow instantaneous sampling of multiple colour patches, and can produce highly repeatable images (McKay 2013). The main challenges for gathering and using color data from photographs are ensure correct standardization methods such as linearization and consistent lighting (Stevens et al. 2007; ref Dariella Whitiyev 2014’s paper). Crucially, most digital cameras used in color science are consumer products designed for human visual color space and hardware modifications for ultraviolet and infrared imaging are necessary (e.g. Chiao et al. 2009, McKay 2013), making photography complementary, rather than superior to spectrophotometry.

@@

###Table 1
```{r, eval = TRUE, echo = FALSE}
tab1 <- read.csv("/Users/danielnoble/Dropbox/6_Share_Folder/colsci_rep/output/tables/table1.csv", header = TRUE)
table1 <- xtable(tab1)
print(table1, type = "pdf")
```
##What is reporting like in the literature? (what do people do?)

To determine the current state of methods reporting in the field we searched for papers from 2013 in 20 journals (see Table X): We used the Boolean search terms colour*, color* or spectra* and searched for these in the title or abstract from each of the journal home pages. Our search returned a total of X papers. To review the large number of papers returned from the searches, journals were haphazardly divided up between the authors. Upon reading abstracts we determined which studies took empirical measures of colour (via photography or spectrophotometry) and discarded those that did not. In order to reduce the risk of observer bias in our scoring. Papers were then read and reassessed by a second author and a third, three times in total. Any discrepancies between the assessor scores and the inclusion of papers with more obscure or uncommon methodologies, were discussed and agreed upon. We then tabulated what details of the methods were reported against our criteria.
